Leader functions and qualities across 59 cultures: an exploratory analysis

### 2019-11-27 leadership_across_cultures_contexts.Rmd

>>>>

## Distribution of text records by mode of subsistence and group type

The type of group to which a leader text referred was coded into seven categories. Figure \@ref(fig:groupsex) indicates the proportion of text records that were categorized into each of these groups.

```{r groupsex, fig.width=20, fig.height=10, fig.cap="The distribution of text records by subsistence and group type. Areas of the bars are proportional to the number of text records in that category."}
plot_group_subsis #+ plot_group_sex
```
